# Reproducible Research: Peer Assessment 1
In this assignment, the data from activity trackers is analyzed and documented
in a kntr report.

## Loading and preprocessing the data
1. The activity zip files has to be downloaded and extracted in the working directory
2. The file contains headers and 3 columns: steps, date and interval
3. The missing values in the steps column are indicated by an "NA" string

```{r echo=TRUE} 
df <- read.csv("activity.csv", 
               header=TRUE, 
               sep=",",
               na.strings=c("NA"),
               colClasses=c("numeric", "Date", "numeric"))
df$interval <- factor(df$interval)
```

The examination of the data reveals, there are no additional
step to preprocess the data are necessary.
  
```{r funct_read, echo=TRUE} 
summary(df)
head(df)
str(df)
```


## What is mean total number of steps taken per day?

Total Steps
```{r echo=TRUE} 

library(ggplot2)

aggdf <- aggregate( df$steps, by=list(df$date), FUN=sum,na.rm=TRUE)
names(aggdf)[1]<-paste("Date")
names(aggdf)[2]<-paste("No_of_Steps")
steps_mean <- round(mean(aggdf$No_of_Steps))
steps_median <- median(aggdf$No_of_Steps)
ggplot(aggdf, aes(x=No_of_Steps)) + 
      geom_histogram(fill="red", binwidth=2000) +
      geom_vline(xintercept=steps_mean, color="blue") +
      geom_vline(xintercept=steps_median, color="green")


```

**number of steps per day:**  
**`r paste("mean ", steps_mean, " (blue) ")`**
**`r paste("median ", steps_median, " (green)")`**

